Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters

### 2023-07-02 report/report.tex
first paper draft
polished report

We propose to circumvent these challenges by leveraging state-of-the-art language models to transform companies' highly informative public text data into machine-readable data points, and then applying clustering to identify market segments and make location recommendations for novel companies to support business cluster development.

@@

Deciding on the location of a business is a vital strategic decision. Finding the right location can have several benefits: First, it is crucial to most businesses to be located close to their customers and suppliers for more effective marketing or reduced transportation costs. Secondly, being located in an active regional cluster can significantly benefit a business development \cite{clustersandcomp,gems-model, regionaladv, clustertheory}.

Business clusters are local concentrations of businesses, manufacturers, suppliers, and institutions from the same field. Identifying regional clusters is done by combining geographical data of companies' locations with information on their corresponding market segments. This geographic proximity of related businesses enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all businesses within the cluster \cite{clustersandcomp,gems-model, regionaladv, clustertheory}. Thus, establishing or further developing business clusters is of high interest to companies and local governments. Therefore, significant effort is spent identifying clusters and market segments in regional economies.

@@

This process is very labor-intensive, as businesses do not provide specific data on the latter points, but it must be inferred from their product portfolio and websites. Additionally, even simpler data like the number of employees is often unavailable or only available inside hard-to-parse company websites, especially for small regional companies.

@@

The main contribution of this work is an automatic clustering pipeline to effectively identify market segments and business clusters from publicly available information. Utilizing those clusters, our system can provide a strategic location, which we will demonstrate by using the German federal state Saarland as an example. The novelty of our approach is that we rely on language models to process the companies' information.

Our clustering pipeline can be divided into $4$ distinct steps: $1)$ gathering data from the websites of companies in Saarland, $2)$ computing embeddings of the data, $3)$ reducing the embeddings' dimensionality, and $4)$ applying clustering algorithms.

@@

$4)$ Lastly, we apply well-established clustering algorithms in the low-dimensional feature space to assign each company to a cluster corresponding to a potential market segment.

@@

\section{Related Work}
In this section, we will examine previous work on business clusters, and recent advances in natural language processing.

@@

Business clusters and their advantages have been studied in many works. For example, \cite{regionaladv} examined the well known technology cluster in the Silicon Valley, famous for being the home of many innovative startups even in recent years.

\cite{clustertheory} provides detailed discussion of the cluster phenomenon. It discusses preexisting literature on clusters and reviews the two main postivies effects commonly observed in clusters, positive feedback, and productivity \& growth. Additionally, it provides examples for well-known clusters.

Our region of choice for testing our approach, Saarland, has also been subject of scientific work. It should be noted that most of them examine it for its location on the border of France and Luxembourg or because of its mining and steel producing past.

These factors are however of no interest to this work. For example, \cite{saarlandeco1} has focused on the agglomeration of automotive industry in Saarland and the neighboring regions, but focuses on the challenges that the country borders pose to this industry.

The paper \cite{saarlandeco2} specifically compares the economic strategies for development of the regions economy and with a focus on how clusters are developed. Most importantly, they identify some regional clusters. We will revisit these when evaluating our clustering algorithm and compare on the clusters identified by our approach. It should be noted however that the paper was published in 2009, therefore the analysis conducted by this paper was based on the economy at least 14 years before this paper.

@@

\textit{$1)$ Collect Descriptions:} The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector. However, it is generally unclear which are the best attributes for representing companies. Further, it is not straightforward to encode non-numerical attributes, like products and customer base, so clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values. 
Lastly, some attributes may be unavailable for some companies, meaning we would need to discard them because we require fixed-size vectors, or we would need to insert dummy values, which could lead to unwanted effects.
To address these challenges to dataset construction, we propose representing companies by the description on their websites instead of numerical attributes. The benefit of using this data is that, since companies design their website to attract customers and investors, they include detailed information, such as their products, market positioning, and customer base. Using the text directly circumvents the problem of creating a targeted aggregator for specific information. This makes our approach simpler to implement and a lot more scalable \& automatable for larger target regions.

@@

\textit{$3)$ Projection into 2D / 3D Space:} Although the embeddings are of much lower dimensionality than the original text data, the number of features might still be too large relative to the size of our dataset. This might invoke the curse of dimensionality, meaning that the few data points are so distant from each other in the high-dimensional space that it is impossible to derive meaningful clusters. Further, clustering data in high-dimensional space prevents the visualization of clustered data points. To avoid the course of dimensionality and to enable user-friendly visualization of our results, we will project the embeddings to 2D or 3D space using two dimensionality reduction techniques.

@@

\textit{$4)$ Clustering:} We will now present two clustering approaches that depend on the choice of dimensionality reduction technique.
If KPCA is used, we cluster the data using the $K$-Means algorithm, which, starting from $K$ randomly initialized cluster centers, assigns each data point to the nearest cluster, updates the values of the cluster centers as the mean of each data point in the cluster, and then repeats until the cluster assignments do not change anymore. We combine $K$-Means with KPCA since it returns a set of cluster centers that can be used to classify novel data points. 
If t-SNE is used, we cluster the data using agglomerative clustering, which initially assigns each data point to a separate cluster and then iteratively merges close clusters until all data points are in the same cluster. The intermediate clustering that achieves the largest overall separation between data points can then be chosen as the final clustering. The advantage of agglomerative clustering over $K$-Means is that it does not require a pre-specified number of clusters and can compute hierarchically structured clusters.
Once the clustering algorithm converges, we receive cluster labels for each company in our dataset, corresponding to the predicted market segments.

@@

Figure \ref{fig:clustering-analysis} depicts the clustering analysis tab of our user-interface. On the left side, users can define how the description embeddings are computed, the technique and target dimensionality of the dimensionality reduction, and the number of clusters. Additionally, users can specify a subset of additional features, including industry, products, customer base, market positioning, and revenue, which will be combined with the descriptions. After clicking "Compute clustering", the clustered data points are shown on the right side as a 2D or 3D scatter plot. Further, users can see the location and clustering assignment of all companies in our dataset on a map. When hovering the mouse over a company's data point, additional information about the company is shown, and when double clicking the labels on the legend, only the companies of the corresponding cluster are shown.

@@

\subsection{Fostering Business Clusters through Location Recommendations}
We utilize parts of our clustering pipeline to give location recommendations for companies seeking to establish new sites in Saarland. Given the description of the novel company, we compute an embedding using a sentence transformer and apply KPCA or t-SNE to get a low-dimensional feature vector. We then assign the feature vector to a cluster according to the $K$-Means or agglomerative clustering algorithm and then compute which company within the cluster is most similar to the novel company. Note that when using KPCA and $K$-Means, we can assign the novel data points to a pre-computed clustering, and when using t-SNE and agglomerative clustering, we compute a new clustering.
Thus, the second approach accounts for the possibility that introducing a novel company might change existing market segments, whereas the first approach does not.
Given the cluster label of the novel company, the location recommendation is to establish the new company site nearby the most similar company within the cluster, meaning we recommend placing the novel site near the most similar company acting in the same market segment. Thus, our location recommendations support the geographical concentration of companies acting in the same market segment, which helps to foster business clusters in Saarland.

Our user-interface offers a dedicated tab for location recommendations. In figure \ref{fig:location-recommendation-input} we see the text boxes where users can provide their company's name and description. Additionally, users can specify their company's industry, products, customer base, market position, and revenue which can be used to support the location recommendations. After clicking "Submit", users are shown the output depicted in figure \ref{fig:location-recommendation-output}. The table at the top shows the names and features of the companies in the cluster, to which the user's company was assigned. The scatter plot at the bottom left shows the clustered data points, where the point of the user's company is highlighted. Lastly, the map at the bottom right displays the location of the novel company's cluster members and the distances between them. The user can also overlay a heatmap which show the similarity between his company and all other companies in out dataset.

@@

\section{Experiments}
To build our dataset of company descriptions, we manually extracted the descriptions of $50$ of the largest companies in Saarland. When a description was only available in German, we translated it to English using the online translator DeepL. A list of all companies in our dataset can be found in the appendix \ref{sec:appendix-companies}.

For the purpose of the experimental evaluation we conducted the data collection manually. As our target region was very narrow this was easily feasible. However, in the future we might create a simple HTML scraper to scale our approach to larger regions. To test our location recommendation feature, we created company descriptions using GPT-4 \cite{chatgpt}.

Additionally, we evaluate the impact of providing additional features to the clustering pipeline, for which also gathered the features industry, products, customer base, market positioning, and revenue of each company.

We utilize the popular pre-trained sentence transformer model "all-MiniLM-L6-v2" from the HuggingFace hub~\cite{sentence-transformer-model} to compute sentence embeddings for each description. An embedding for the full description is then attained using our concatenation, average, or max pooling approach. When using additional features, we compute embeddings for each feature and combine them with the description embedding in the same way the individual sentence embeddings were combined.
Afterward, the embeddings are projected onto 2D or 3D space using KPCA or t-SNE. We chose suitable hyperparameters for KPCA by conducting a grid search over the values $\textit{kernel} = \{\textit{radial basis function}, \textit{sigmoid}, \textit{linear}, \textit{polynomial} \}$ and $\textit{gamma} = \{0.03, 0.032, 0.034, \dots, 0.05\}$, where we found the best values to be $\textit{kernel} = \textit{polynomial}$ and $\textit{gamma} = 0.05$. For t-SNE, we manually fine-tuned the perplexity hyperparameter until we achieved a suitable separation of data points.

@@

In the following, we will investigate the results of the best-performing configuration of our clustering and location recommendation system. These results were obtained using the following configuration: the description embeddings were computed using max pooling, the embeddings were projected into 2D space using t-SNE, and the clustering was achieved using agglomerative clustering. We also used the companies' industry as an additional feature.
 We found that this configuration yields the most sensible predictions of market segments and location recommendations. Figure \ref{fig:t-sne-agglomerative} displays the resulting clustered data points.

@@

\begin{itemize}
	\item Coal and mining industries: With the decline of coal mining in recent years, there are no more coal mines in Saarland. As the last one closed in 2012, this cluster does not exist anymore. 
	\item Metal industry: Covered by cluster 1 (light green) and cluster 6 (yellow).
	\item Automobile industry: Covered by cluster 0 (red).
	\item Energy sector: Covered by cluster 5 (light blue).
	\item Information and communication technology: Covered by cluster 3 (beige).
	\item Biotechnology and nanotechnology: Covered by cluster 2 (dark blue).
\end{itemize}

One can see that the results of our pipeline do agree with the general sectors identified by \cite{saarlandeco2}. However, our approach did lead to more fine-grained separation. Additionally, we identified sectors not covered in their work, such as cluster 7 which represents the construction work market segment. However, these sectors are usually not contributing significantly to the region's economy, which is most probably why they are not mentioned in \cite{saarlandeco2}. In summary, the output of our pipeline matches very well with traditionally identified clusters.

@@

For FluxAI, our system recommends placing the new site close to CISPA, which is sensible since CISPA is a world leader in information security research, which also includes artificial intelligence, and thus knowledge transfer between both companies could be highly beneficial. It also makes sense that our system did not recommend locating FluxAI near IT companies with a more commercial focus, like SAP, since they primarily work on existing technology instead of revolutionary innovations.
For ABC Auto, the location recommendation is to establish a new site close to VOIT, which specializes in manufacturing car components with a focus on hybrid and electric cars. Thus, placing ABC Auto near VOIT would allow ABC Auto to source parts for its hybrid and electric cars from a company nearby, leading to a more robust supply chain.
For Bratwurst Bliss, the system recommends settling near the meat producer Kunzler, which could lead to knowledge transfer regarding sausage making.
Lastly, our system recommends placing PanzerTech's new site close to Diehl Defence, corresponding to the only weapons manufacturer in our dataset. Hence, this shows that our system does not need a large number of samples from each market segment to give reasonable location recommendations.

@@

\section{Conclusion}
The goal of this project was to collect data on companies in Saarland and apply clustering algorithms such that the results can be used to identify regional clusters and give location recommendations for novel companies such that business clusters are fostered.

To circumvent the challenges of feature selection and encoding non-numerical features, we represented companies by their publicly available descriptions. We leveraged state-of-the-art language models to transform this highly informative text data into machine-readable embeddings. Lastly, we utilized two approaches to project the embeddings into low-dimensional space where clustering can be applied.
Further, our methods allowed straightforwardly including other standard company attributes, such as industry, customer base, market positioning, and revenue. 
To make location recommendations, we passed the descriptions and features of novel companies to our clustering pipeline and then recommended establishing new sites next to the most similar companies in our dataset.

A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer major industry segments in Saarland. Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company, independently of the total number of similar companies in the dataset.

@@

We see many opportunities for future work. Collecting data from more companies in Saarland could improve the clustering results, although the number of (large) companies in Saarland is limited. Thus, applying our methods to larger economies would be of great interest. This would also allow more comparisons to traditionally identified clusters. Further, fine-tuning our language models using text data from the business sector might lead to more expressive embeddings. To achieve this, efficiently, an automated aggregation system could be developed. As we utilize publicly available websites, this would be easily possible without relying on 3rd party services.
To this end, we have demonstrated the feasibility and potential of applying language models to economic analysis.

@@

\newpage
\appendix
\nm{Upload all \LaTeX{} files to overleaf when its done since they want a link! Update readme in repo!}
\begin{itemize}
	\item \textbf{Link to Code}: Provide the link to your code repository. You can use any service to host your code (Github, gdrive etc.). The code should be running, accessible and all of your work must be reproducible. In case your code is not accessible or not in a working state, relevant number of points will be deducted.   
	\item \textbf{Link to Overleaf}: Add a link to the Overleaf project which contains all of the LaTex related files for this report.
	\item \textbf{Additional Figures}: Add any and all additional figures produced during you work with relevant explanations in the appendix.
\end{itemize}

\subsection{Additional Clustering Results}

\subsection{Link to Code}
\url{https://github.com/NicolaMueller42/data_science_project}

>>>>

	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform companies' highly informative public text data into machine-readable data points and then applying clustering to identify market segments and make location recommendations for novel companies to support business cluster development.

@@

Deciding on the location of a business is a vital strategic decision. Finding the right location can have several benefits: First, it is crucial for most businesses to be located close to their customers and suppliers for more effective marketing or reduced transportation costs. Secondly, being located in an active regional cluster can significantly benefit a business development \cite{clustersandcomp,gems-model, regionaladv, clustertheory}.

Business clusters are local concentrations of businesses, manufacturers, suppliers, and institutions from the same field. Identifying business clusters is done by combining geographical data of companies' locations with information on their corresponding market segments. This geographic proximity of related businesses enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all businesses within the cluster \cite{clustersandcomp,gems-model, regionaladv, clustertheory}. Thus, establishing or further developing business clusters is of high interest to companies and local governments. Therefore, significant effort is spent identifying clusters and market segments in regional economies.

@@

This process is very labor-intensive, as businesses do not provide specific data on the latter points, but it must be inferred from their product portfolio and websites. Additionally, even basic data like the number of employees is often unavailable or difficult to extract automatically, especially for small regional companies.

@@

The main contribution of this work is an automatic clustering pipeline to effectively identify market segments and business clusters from publicly available information. Utilizing those clusters, our system can provide a strategic location recommendation, which we will demonstrate by using the German federal state Saarland as an example. The novelty of our approach is that we rely on language models to process the companies' information.

Our clustering pipeline can be divided into $4$ distinct steps: $1)$ gathering descriptions from the websites of companies, $2)$ computing embeddings of the text data, $3)$ reducing the embeddings' dimensionality, and $4)$ applying clustering algorithms.

@@

$4)$ Lastly, we apply well-established clustering algorithms in the low-dimensional feature space to assign each company to a cluster from which a potential market segment can be inferred.

@@

\section{Related Work}
This section will examine previous work on business clusters and recent advances in natural language processing.

@@

Business clusters and their advantages have been studied in many works. For example, \cite{regionaladv} examined the well-known technology cluster in Silicon Valley, famous for being the home of many innovative start-ups.

\cite{clustertheory} provides a detailed discussion of the cluster phenomenon. It discusses preexisting literature on clusters and reviews the two main positive effects commonly observed in clusters, i.e., positive feedback and productivity \& growth. Additionally, it provides examples of well-known clusters.

The region of choice for testing our approach, Saarland, has also been the subject of scientific work. It should be noted that most of them examine it for its location on the border of France and Luxembourg or because of its mining and steel-producing past.

These factors are, however, of no interest to this work. For example, \cite{saarlandeco1} has focused on the agglomeration of the automotive industry in Saarland and the neighboring regions but focuses on the challenges that the country borders pose to this industry.

The paper \cite{saarlandeco2} specifically compares the economic strategies for developing the region's economy with a focus on how business clusters are developed. Most importantly, they identify some business clusters. We will revisit these when evaluating our clustering algorithm and compare them to the clusters identified by our approach. It should be noted, however, that the paper was published in 2009, therefore the analysis could be outdated.

@@

\textit{$1)$ Collect Descriptions:} The traditional approach for building an economic dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector. However, it is generally unclear which are the best attributes for representing companies. Further, it is not straightforward to encode non-numerical attributes, like products and customer base, so clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values. 
Lastly, some attributes may be unavailable for some companies, meaning we would need to discard them because we require fixed-size vectors, or we would need to insert dummy values, which could lead to unwanted effects.
To address these challenges to dataset construction, we propose representing companies by the description on their websites instead of numerical attributes. The benefit of using this text data is that, since companies design their website to attract customers and investors, they include detailed information, such as their industry, products, market positioning, and customer base. Hence, we circumvent the problem of creating a targeted aggregator for specific information. This makes our approach simpler to implement and significantly more scalable \& automatable for larger target regions.

@@

\textit{$3)$ Projection into 2D / 3D Space:} Although the embeddings are of much lower dimensionality than the original text data, the number of features might still be too large relative to the size of our dataset. This might invoke the curse of dimensionality, meaning that the few data points are so distant from each other in the high-dimensional space that it is impossible to derive meaningful clusters. Further, clustering data in high-dimensional space prevents the visualization of clustered data points. To avoid the course of dimensionality and to enable user-friendly visualization of our results, we will project the embeddings to 2D or 3D space using two dimensionality reduction techniques:

@@

\textit{$4)$ Clustering:} We will now present two clustering approaches that depend on the choice of dimensionality reduction technique.
If KPCA is used, we cluster the data using the $K$-Means algorithm, which, starting from $K$ randomly initialized cluster centers, assigns each data point to the nearest cluster, updates the values of the cluster centers as the mean of each data point in the cluster, and then repeats until the cluster assignments do not change anymore. We combine $K$-Means with KPCA since it returns a set of cluster centers that can be used to classify novel data points. 
If t-SNE is used, we cluster the data using agglomerative clustering, which initially assigns each data point to a separate cluster and then iteratively merges close clusters until all data points are in the same cluster. The intermediate clustering that achieves the largest overall separation between data points can then be chosen as the final clustering. The advantage of agglomerative clustering over $K$-Means is that it does not require a pre-specified number of clusters and can compute hierarchically structured clusters.
Once the clustering algorithm converges, we receive cluster labels for each company in our dataset, allowing us to predict market segments.

@@

Figure \ref{fig:clustering-analysis} depicts the clustering analysis tab of our user-interface. On the left side, users can define how the description embeddings are computed, the technique and target dimensionality of the dimensionality reduction, and the number of clusters. Additionally, users can specify a subset of additional features, including industry, products, customer base, market positioning, and revenue, which will be combined with the descriptions. After clicking "Compute clustering", the clustered data points are shown on the right side as a 2D or 3D scatter plot. Further, users can see the location and clustering assignment of all companies in our dataset on a map. When hovering the mouse over a company's data point, additional information about the company is shown, and when double-clicking the labels on the legend, only the companies of the corresponding cluster are shown.

@@

\subsection{Fostering Business Clusters through Location Recommendations}
We utilize parts of our clustering pipeline for recommending locations for companies seeking to establish new sites in Saarland. Given the description of the novel company, we compute an embedding using a sentence transformer and apply KPCA or t-SNE to get a low-dimensional feature vector. We then assign the feature vector to a cluster according to the $K$-Means or agglomerative clustering algorithm and then compute which company within the cluster is most similar to the novel company. Note that when using KPCA and $K$-Means, we can assign the novel data points to a pre-computed clustering, and when using t-SNE and agglomerative clustering, we compute a new clustering.
Thus, the second approach accounts for the possibility that introducing a novel company might change existing market segments, whereas the first approach does not.
Given the cluster label of the novel company, the location recommendation is to establish the new company site nearby the most similar company within the cluster, meaning we recommend placing the novel site near the most similar company acting in the same market segment, which helps to foster business clusters in Saarland.

Our user-interface offers a dedicated tab for location recommendations. In figure \ref{fig:location-recommendation-input}, we see the text boxes where users can provide their company's name and description. Additionally, users can specify their company's industry, products, customer base, market position, and revenue, which can be used in the location recommendations. After clicking "Submit", users are shown the output depicted in figure \ref{fig:location-recommendation-output}. The table at the top shows the names and features of the companies in the cluster to which the user's company was assigned. The scatter plot at the bottom left shows the clustered data points, where the point of the user's company is highlighted. Lastly, the map at the bottom right displays the location of the novel company's cluster members and the distances between them. The user can also overlay a heatmap that shows the similarity between his company and all other companies in our dataset.

@@

\section{Experiments}
To build our dataset of company descriptions, we manually extracted the descriptions of $50$ of the largest companies in Saarland. When a description was only available in German, we translated it to English using the online translator DeepL~\cite{deepl}. A list of all companies in our dataset can be found in the appendix \ref{sec:appendix-companies}.

For the purpose of the experimental evaluation, we conducted the data collection manually. As our target region was very narrow, this was easily feasible. However, in the future, we might create a simple HTML scraper to scale our approach to larger regions. To test our location recommendation feature, we created company descriptions using GPT-4 \cite{chatgpt}.

Additionally, we evaluate the impact of providing additional features to the clustering pipeline, for which we also gathered the features industry, products, customer base, market positioning, and revenue of each company.

We utilize the popular pre-trained sentence transformer model "all-MiniLM-L6-v2" from the HuggingFace hub~\cite{sentence-transformer-model} to compute sentence embeddings for each description. An embedding for the full description is then attained using our concatenation, average, or max pooling approach. When using additional features, we compute embeddings for each feature and combine them with the description embedding in the same way the individual sentence embeddings were combined.
Afterward, the embeddings are projected into 2D or 3D space using KPCA or t-SNE. We chose suitable hyperparameters for KPCA by conducting a grid search over the values $\textit{kernel} = \{\textit{radial basis function}, \textit{sigmoid}, \textit{linear}, \textit{polynomial} \}$ and $\textit{gamma} = \{0.03, 0.032, 0.034, \dots, 0.05\}$, where we found the best values to be $\textit{kernel} = \textit{polynomial}$ and $\textit{gamma} = 0.05$. For t-SNE, we manually fine-tuned the perplexity hyperparameter until we achieved a suitable separation of data points.

@@

In the following, we will investigate the results of the best-performing configuration of our clustering and location recommendation system. These results were obtained using the following configuration: the description embeddings were computed using max pooling, the embeddings were projected into 2D space using t-SNE, and the clustering was achieved using agglomerative clustering. We also used the companies' industry as an additional feature.
We found that this configuration yields the most sensible clusters and location recommendations. Figure \ref{fig:t-sne-agglomerative} displays the resulting clustered data points.

@@

\begin{itemize}
	\item \textit{Coal and mining industries}: With the decline of coal mining in recent years, there are no more coal mines in Saarland. As the last one closed in 2012, this cluster does not exist anymore. 
	\item \textit{Metal industry}: Covered by cluster 1 (light green) and cluster 6 (yellow).
	\item \textit{Automobile industry}: Covered by cluster 0 (red).
	\item \textit{Energy sector}: Covered by cluster 5 (light blue).
	\item \textit{Information and communication technology}: Covered by cluster 3 (beige).
	\item \textit{Biotechnology and nanotechnology}: Covered by cluster 2 (dark blue).
\end{itemize}

One can see that the results of our pipeline do agree with the general sectors identified by \cite{saarlandeco2}. However, our approach did lead to more fine-grained separation. Additionally, we identified sectors not covered in their work, such as cluster 7, which represents the construction work market segment. However, these sectors usually do not contribute significantly to the region's economy, which is probably why they are not mentioned in \cite{saarlandeco2}. In summary, the output of our pipeline matches very well with traditionally identified clusters.

@@

For FluxAI, our system recommends placing the new site close to CISPA, which is sensible since CISPA is a world leader in information security research, which also includes artificial intelligence, and thus knowledge transfer between both companies could be highly beneficial. It also makes sense that our system did not recommend locating FluxAI near IT companies with a more commercial focus, like SAP, since they primarily work on existing technology instead of revolutionary innovations.
For ABC Auto, the location recommendation is to establish a new site close to VOIT, which specializes in manufacturing car components with a focus on hybrid and electric cars. Thus, placing ABC Auto near VOIT would allow ABC Auto to source parts for its hybrid and electric cars from a company nearby, leading to a more robust supply chain.
For Bratwurst Bliss, the system recommends settling near the meat producer Kunzler, which could lead to knowledge transfer regarding sausage-making.
Lastly, our system recommends placing PanzerTech's new site close to Diehl Defence, corresponding to the only weapons manufacturer in our dataset. Hence, this shows that our system does not need a large number of samples from each market segment to give reasonable location recommendations.

@@

\section{Conclusion}
The goal of this project was to collect data on companies in Saarland and apply clustering algorithms such that the results can be used to identify market segments and give location recommendations for novel companies such that business clusters are fostered.

To circumvent the challenges of feature selection and encoding non-numerical features, we represented companies by their publicly available descriptions. We leveraged state-of-the-art language models to transform this highly informative text data into machine-readable embeddings. Lastly, we utilized two approaches to project the embeddings into low-dimensional space where clustering can be applied.
Our methods allowed straightforwardly including other standard company attributes, such as industry, customer base, market positioning, and revenue. 
To make location recommendations, we passed the descriptions and features of novel companies to our clustering pipeline and then recommended establishing new sites next to the most similar companies in our dataset.

A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer market segments in Saarland. Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company, independently of the total number of similar companies in the dataset.

@@

We see many opportunities for future work. Collecting data from more companies in Saarland could improve the clustering results, although the number of (large) companies in Saarland is limited. Thus, applying our methods to larger economies would be of great interest. This would also allow more comparisons to traditionally identified clusters. Further, fine-tuning our language models using text data from the business sector might lead to more expressive embeddings. To achieve this efficiently, an automated aggregation system could be developed. As we rely on publicly available websites, this would be easily possible without relying on 3rd party services.
To this end, we have demonstrated the feasibility and potential of applying language models to economic analysis.

@@

\newpage
\appendix
\nm{Upload all \LaTeX{} files to overleaf when its done since they want a link!}
\subsection{Link to Code}
\url{https://github.com/NicolaMueller42/data_science_project}
